Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-02 05-evaluation.tex
More reorganization and adding Makefile
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@847 df1a90cd-247b-4364-bdaf-287a704eb499

\todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}

>>>>

% \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}
